### 2014-12-24 paper_30_measure.tex
fixed Schedule chapter problem starting to work on SEMAT section
adding book how to measure anything
descriptions for indicators

\section{DATA DRIVEN SOFTWARE ENGINEERING}

Performance indicators can be crucial measurements
within any business setting, and an SDO is no exception. Many
SDOs struggle to determine the correct indicators to track and
how to track them.  
The differences between the indicators will be explored and
possible measures for each indicator in an SDO will be
presented.  The 4 different types of indicators are.
\begin{enumerate}
  \item RI (Result Indicator)
  \item KRI (Key Result Indicator)
  \item PI (Performance Indicator)
  \item KPI (Key Performance Indicator)
\end{enumerate}

>>>>

\section{DATA-DRIVEN SOFTWARE ENGINEERING}

Anything can be measured \cite{Hubbard2010}.

Data Driven Software Engineering not Data Driven Software Development

Performance indicators can be crucial measurements
within any business setting, and an SDO is no exception. Many
SDOs struggle to determine the correct indicators to track and
how to track them.  
The differences between the indicators will be explored and
possible measures for each indicator in an SDO will be
presented.  The 4 different types of indicators are:
\begin{description}
  \item[RI (Result Indicator)] - what has been done
  \item[KRI (Key Result Indicator)] - how you have done
  \item[PI (Performance Indicator)] - what to do
  \item[KPI (Key Performance Indicator)] - what to do to dramatically increase performance
\end{description}
